Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-21 paper/main.tex
Down from 50 to 35 pages
Turn off note renderin
shorten anterior vs posterior

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{todonotes}
\usepackage{units}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\todo[inline]{parts from original studies probably too detailed}

\todo[inline]{current order of subsections might be ``non-canonical''}

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ) or a setting as whole
(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
field''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``Jenny as a teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

\todo[inline]{currently table is to wide; smaller font? less text? rotate the
table?}

@@

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.\todo{cautious phrasing but still problematic: looking for
confirmation}
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.

@@

\subsection{Group results (all AO + AV PPA contrasts)}

\todo[inline]{subheadings are still in for better readability; structure could
be changed; at the moment its AO (PPA in primary contrast, robustness of PPA;
other clusters across contrasts), then the same for AV}

@@

\subsubsection{PPA in AO: primary contrasts}

@@

\subsubsection{PPA in AO: robustness across contrasts}

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created seven additional
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
Six of the overall eight AO contrasts show significant bilateral clusters in
anterior regions of the group PPA overlap (see Figure
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed
contrasts.\ref{fig:stability-slices}).\todo[inline]{Discussion: discuss that
contrasts make ``less and less'' sense}
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}
% question 2

@@

\subsubsection{other sign. clusters across AO contrasts}
% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess}
% ventral precuneus = retrosplenial cortex?
7 contrasts: bilateral clusters in RSC (and ventral precuneus);
% transverse occipital sulcus = occipital place area
6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
are more lateral; AV: clusters are more medial}
% confounds
4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
gyrus; 3 contrasts: some (smallish) prefrontal clusters

\subsubsection{PPA in AV: primary contrasts}
% AV intro
Second as conceptual/cross-modal control of the group average results, we
analyzed data from the audio-visual movie by contrasting different kinds of
movie cuts independent(ly) from the frames' visual content following the cuts.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises (reported from posterior to
anterior), parts of the intracalcarine and cuneal cortex, the lingual gyrus and
retrosplenial cortex, the occipital and temporal fusiform gyrus and the
parahippocampal cortex in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

@@

\subsubsection{PPA in AV: robustness + other clusters across contrasts}

% all eight AV PPA contrasts
Here again in order to test the robustness of our findings, we created four
additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters (in
that overlap with the PPA group mask/overlap [biggest overlap in posterior part
of group ROI = temporal occipital fusiform cortex] (see Figure
\ref{fig:stability-slices}).
% concluding statement
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% question
\todo[inline]{concluding statement = interpretation/discussion?}

\subsection{negative controls in AO and AV}

@@

\todo[inline]{the structure is as follows at the moment: correlation of
regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
other clusters significant across contrasts (= retrosplenial cortex and
occipital place area)}

@@

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo should be a small section anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements(, or
memory).\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not do their fucking
job (still, it is kinda innate in the contrast).\todo{the word ''fuck`` is not
acceptable}
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).

% intro to connectivity and object gradient
Kind of complete overview of (references): Previous studies suggest that
posterior and anterior part of the PPA show differences in
% connectivity
a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
Nasr et al., 2013; Silson et al., 2016a],
% scenes vs abstract objects
b) a gradient in sensitivity scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential},
% low-level scene features
c) differences in response to low-level scene features [Nasr et al., 2014;
Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
% high-level scene features
d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
and Macevoy, 2015; Marchette et al., 2015],
% TMS
e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}

\paragraph{posterior PPA (pPPA)}

% connectivity
The posterior PPA is more [strongly] functionally connected to the occipital
visual cortex, including lateral occipital cortex (LOC) and transverse occipital
sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
% LOC and TOS
[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape \citep{baldassano2013differential}.]

%
Increased activity within the pPHC during viewing of scenes relative to objects
has been suggested to reflect regional specialization for visuospatial processes
related to the extraction of scene layout information [Epstein,
2008]\citep{baumann2016functional}.

% high-level visual features
Higher-level visual features also drive response patterns in these regions
[Bryan et al., 2016]. They are hypothesized to be involved in extracting visual
environmental features that can be used for navigation [Marchette et al., 2015;
Julian et al., 2016; Kamps et al., 2016]. However, neither OPA nor posterior PPA
show reliable familiarity effects [Epstein et al., 2007b; see further discussion
below]\citep{baldassano2016two}.
%
The idea that the pPHC serves a dedicated role in visuospatial processing is
further supported by studies showing that this brain region is sensitive to
changes in basic visuospatial properties such as the shape and spatial frequency
of abstract geometric objects and layouts [Rajimehr et al., 2011; Zeidman et
al., 2012]\citep{baumann2016functional}.

% object sensitivity
The pPPA is more responsive to both simple visual textures and (abstract)
objects \citep{arcaro2009retinotopic, baldassano2013differential}:
%
The pPPA responded about four times as strongly to a
flickering checker-board stimulus compared to an anterior portion
\citep{arcaro2009retinotopic}.
%
The response to objects was greater than the
response to scrambled images only in the posterior portion
\citep{arcaro2009retinotopic}.

% low-level features
OPA and pPPA have been shown to be closely related to the visual content of a
stimulus. Even low-level manipulations of spatial frequency [Rajimehr et al.,
2011; Kauffmann et al., 2015; Watson et al., 2016] or rectilinearity [Nasr et
al., 2014] can drive responses in these regions \citep{baldassano2016two}.

% baumann2016functionl
We observed that pPHC is more strongly modulated bilaterally by the visual
properties of the stimulus material (as evidenced by strong responses in the
picture-scene conditions and no significant response in the word-object
conditions)\citep{baumann2016functional}.
%
Our current study [and findings of Baldassano et al. (2013)] suggest that the
functional topographic segregation of the PHC is underpinned by corresponding
segregated connectivity patterns. Findings are consistent with a model of
parahippocampal function in which visual information is projected from occipital
and temporal areas to the pPHC [Libby et al., 2012], where encoding of
visuospatial information takes place (a process that is computationally more
demanding for complex stimuli such as scenes than for simple ones such as
objects; Chai et al., 2010)\citep{baumann2016functional}.

\paragraph{posterior network}

% baldassano2016two
The 1st (posterior) network [of two networks] includes
pPPA and OPA/TOS. pPPA (retinotopic maps PHC1 \& PHC2) and OPA/TOS contain
retinotopic maps and are not strongly coupled to the hippocampus at rest
\citep{baldassano2016two}.

% baldassano20160two: Neurosynth meta-analysis
\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
future'' (125 studie).

%
Results: voxels significant only in the scene meta-analysis were concentrated in
the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
other) % baldassano2016two: meta-analysis
\citep{baldassano2016two} Voxels significant in both the scene and
memory/navigation meta-analyses tended to fall near the border between the two
networks and divided approximately equally among them (44\% posterior, 53\%
anterior, 4\% other).
%
\citep{baldassano2016two} Voxels significant only in the memory/navigation
meta-analysis were spread more widely across the cortex, but were concentrated
more in the anterior than the posterior network (16\% posterior, 42\% anterior,
42\% other).

% interpretation
Interpretation: visual scene activations tend to be posterior to the memory
activations along the parahippocampal gyrus. [The transition point corresponds
almost exactly to the division between our two networks. Dorsally, we also
observe a separation between the reverse inference maps, with scene and memory
activations falling into our two separate networks \citep{baldassano2016two}.]

\paragraph{anterior PPA (aPPA)}

The specific properties of aPPA have been less well studied, since it was not
recognized as a separate region within the PPA until recently
\citep{baldassano2016two}.

% anterior PPA
The anterior PPA is more [strongly] functionally connected to the RSC and
parietal cortices (caudal inferior parietal lobe; cIPL)[, medial PFC, and the
lateral surface of the anterior temporal lobe]
\citep{baldassano2013differential, baldassano2016two}.

% object sensitivity
The aPPA is less visually responsive to both scenes\todo{check their paradigm \&
result section} and objects, with notably low sensitivity to abstract object
stimuli \citep{baldassano2013differential}.
%
Results suggest that aPPA may be more concerned with these types of spatial and
non-object-based scene properties [= global scene properties such as spatial
expanse] than posterior PPA \citep{baldassano2013differential}\todo{check if
quoted correctly}.

\citep{baldassano2016two} The aPPA is
% category
a) driven more by high-level category information than by spatial frequency
content [Watson et al., 2016],
% locations
b) to represent real-world locations (even from perceptually distinct views)[
Marchette et al., 2015],
% associations
c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
% scene size
d) to represent real-world physical scene size [Park et al., 2014]
\citep{baldassano2016two}.
% spaciousness
Its representation of scene spaciousness draws on prior knowledge about the
typical size of different scene categories, since it is affected by the presence
of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.

\paragraph{anterior network}

% baldassano2016two's networks
\citep{baldassano2016two} The anterior network (the 2nd of two networks)
consists of the caudal inferior parietal lobule (cIPL), RSC, and aPPA, which
connect to the hippocampus (especially anterior hippocampus). These regions are
implicated in both visual and nonvisual tasks, including episodic memory and
navigation] \citep{baldassano2016two}.
% baldassano2016connectivity
The anterior network [that includes aPPA] exhibits much higher resting-state
hippocampal coupling (especially to anterior hippocampus), suggesting that
memory- and navigation-related functions are primarily restricted to the
anterior network \citep{baldassano2016two}.

% The memory and navigational network
The network of parahippocampal, retrosplenial, and posterior parietal regions
that we identify has been emerged independently in many different fields of
neuroimaging, outside of scene perception.
%
Meta-analyses of internally directed tasks, such as theory of mind,
autobiographical memory, and prospection, have identified this as a core,
reoccurring network [Spreng et al., 2009; Kim,2010; Yeo et al., 2015 (component
C10 of ?)]. It comprises a subset of the broader default mode regions, but
functional and anatomical evidence suggests that it is a distinct, coherent
subnetwork [Andrews-Hanna et al., 2010, 2014; Yeo et al.,
2011]\citep{baldassano2016two}.
%
The broad set of tasks that recruit this network have been summarized in various
ways, such as ``scene construction'' (Hassabis and Maguire, 2007), ``mnemonic
scene construction'' [Andrews-Hanna et al., 2010], ``long-timescale
integration'' [Hasson et al., 2015], or ``relational processing'' [Eichenbaum
and Cohen, 2014].
%
A review of memory studies referred to this network as the posterior medial
memory system, and proposed that it is involved in any task requiring
``situation models'' relating entities, actions, and outcomes [Ranganath and
Ritchey, 2012]\citep{baldassano2016two}.

% hippocampus
The network has strong functional connections to the hippocampus, which has been
implicated in a broad set of cognitive tasks involving ``cognitive maps'' for
organizing declarative memories, spatial routes, and even social dimensions
[Eichenbaum and Cohen, 2014; Schiller et al., 2015]. During perception, the
hippocampus binds together visual elements of an image [Olsen et al., 2012;
Warren et al., 2012; Zeidman et al., 2015], which is especially important for
scene stimuli [Lee et al., 2005a,b; Graham et al., 2006; Hodgetts et al., 2016].
The hippocamppus then stores this representation into long-term memory [Ryan and
Cohen, 2004]\citep{baldassano2016two}.
%
Our results suggest that only the anterior scene regions interface directly with
the hippocampus, potentially enabling the construction of hippocampal
environmental representations, and retrieval of relevant memories and
navigational information for a presented or imagined
scene\citep{baldassano2016two}.

\paragraph{conclusion \& interpetation: subregions}

% conclusion by Baldassano (2013): PPA subregions
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules.
%
Both subregions activate selectively to scenes, implying that these subregions
cooperate to build a complete representation of a scene
\citep{baldassano2013differential}.

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

@@

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.

@@

\subsection{Group results}

@@

\subsubsection{AO: PPA in primary contrast}

@@

\subsubsection{AO: robustness of PPA across contrasts}

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created seven additional
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
Six of the overall eight AO contrasts show significant bilateral clusters in
anterior regions of the group PPA overlap (see Figure
\ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}
%
\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}

@@

\subsubsection{AO: other significant clusters across contrasts}
% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess}
% ventral precuneus = retrosplenial cortex?
So far, just a short list => 7 contrasts: bilateral clusters in RSC (and ventral
precuneus);
% transverse occipital sulcus = occipital place area
6 contrasts (4 bilateral, 2 unilateral): lateral occipiatal cortex (transverse
occipital sulcus; occipiatal place area?; AO clusters are more lateral, AV
cluster are more medial (\& caudal) but AO \& AV clusters overlap)
% confounds
4 contrasts: right superior temporal gyrus (auditory cortices); 3 contrasts:
left superior temporal gyrus; 3 contrasts: some (smallish) prefrontal clusters

\subsubsection{AV: PPA in primary contrast}
% AV intro
Second as conceptual/cross-modal control of the group average results, we
analyzed data from the audio-visual movie by contrasting different kinds of
movie cuts independent(ly) from the frames' visual content following the cuts.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises (reported from posterior to
anterior), parts of the intracalcarine and cuneal cortex, the lingual gyrus and
retrosplenial cortex, the occipital and temporal fusiform gyrus and the
parahippocampal cortex in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

@@

\subsubsection{AV: robustness of PPA across contrasts}

% all eight AV PPA contrasts
Here again in order to test the robustness of our findings, we created four
additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
[biggest overlap in posterior part of PPA group overlap  = temporal occipital
fusiform cortex] .
% concluding statement
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% question
\todo[inline]{concluding statement = interpretation/discussion?}

\subsubsection{AV: other signficant clusters across contrasts}

\subsubsection{AO \& AV: (negative) control contrasts}

@@

\todo[inline]{structure is as follows: correlation of
regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
other clusters significant across contrasts (= retrosplenial cortex and
occipital place area)}

@@

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo discussion of AV should be short anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements[, or
memory].\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of both the PPA group overlap and significant
clusters of the AV contrasts.

% but
Previous studies suggest that the PPA is not a functionally homogeneous area but
consists of submodules that ``activate selectively to scenes'' and ``cooperate
to build a complete representation of a scene''
\citep{baldassano2013differential}.

%
The anterior and posterior PPA show:
% connectivity
a) differences in connectivity profiles [Nasr et al., 2013; Silson et al.,
2016a] \citep{baldassano2013differential, baldassano2016two},
% low-level scene features
b) different responses to low-level scene features [Nasr et al., 2014; Silson et
al., 2015; Baldassano et al., 2016a,b; Watson et al.,
2016]\citep{baldassano2016two},
% high-level scene features
c) different responses to high-level scene features [Park et al., 2014; Aminoff
and Tarr, 2015; Linsley and Macevoy, 2015; Marchette et al.,
2015]\citep{baldassano2016two},
% scenes vs abstract objects
c) a gradient in functional sensitivity to scenes and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential}, and
% TMS
e) differences in stimulation studies [+++Rafique et al.,
2015+++]\citep{baldassano2016two}.  \paragraph{posterior PPA}

% connectivity
The posterior PPA is more strongly functionally connected to the occipital
visual cortex, including lateral occipital cortex (LOC) and transverse occipital
sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
% LOC and TOS
These regions have well-defined retinotopic maps [+++Arcaro et al., 2009; Nasr
et al., 2011+++], and are associated with the perception of low-level visual
features and object shape \citep{baldassano2013differential}.

% object sensitivity
lower-level features: The pPPA is more responsive to both simple visual textures
and (abstract) objects \citep{arcaro2009retinotopic,
baldassano2013differential}:
%
The pPPA responded about four times as strongly to a flickering checker-board
stimulus compared to an anterior portion \citep{arcaro2009retinotopic}.
%
The response to objects was greater than the response to scrambled images only
in the posterior portion \citep{arcaro2009retinotopic}.

%
high-level features: Higher-level visual features also drive response patterns
in these regions [Bryan et al., 2016].

\paragraph{anterior PPA}

The anterior PPA is more strongly functionally connected to the RSC and parietal
cortices (caudal inferior parietal lobe; cIPL; cIPL was defined using the
Eickhoff–Zilles PGp probabilistic cytoarchitectonic map)[, medial PFC, and the
lateral surface of the anterior temporal lobe]
\citep{baldassano2013differential, baldassano2016two}.

\citep{baldassano2016two} The aPPA is
% category
a) driven more by high-level category information than by spatial frequency
content [Watson et al., 2016],
% locations
b) to represent real-world locations (even from perceptually distinct views)[
Marchette et al., 2015],
% associations
c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
% scene size
d) to represent real-world physical scene size [Park et al., 2014]
\citep{baldassano2016two}.

% object sensitivity
The aPPA is less visually responsive to both scenes and objects, with notably
low sensitivity to abstract object stimuli \citep{baldassano2013differential}.
%
Results suggest that aPPA may be more concerned with global scene properties
(such as spatial expanse) and non-object-based scene properties than posterior
PPA \citep{baldassano2013differential}.

% spaciousness
Its representation of scene spaciousness draws on prior knowledge about the
typical size of different scene categories, since it is affected by the presence
of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.

\paragraph{conclusion: subregions}

%
although our data suggest that PPA might contain identifiable subregions, these
subregions should not be considered as completely independent modules. Both
subregions activate selectively to scenes, and the parahippocampal region (at
least in macaques) is densely self-connected (Suzuki 2009), implying that these
subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, do suggest that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information\citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape. If anterior PPA is involved in processing
spatial context, then space-defining or navigationally-relevant objects could
activate anterior PPA more strongly than our abstract objects, which were
unfamiliar and provided no sense of context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.

\paragraph{contextual associations}

%
The PCH has been implicated in the integration and retrieval of contextual
associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
2008a, 2008b].
%
According to this view, activity in PHC reflects modality-independent retrieval
of contextual information from memory (contextual associations: relations
between objects and conditions that describe, represent, and bring meaning to an
environment; such as which objects typically occur in a given scene and where
they are likely to be located relative to one another; [Aminoff et al., 2013])
\citep{baumann2016functional}.

Results: aPHC is more active during contextual judgments regardless of stimulus
category (scenes vs objects) or modality (word vs picture)
\citep{baumann2016functional}.
%
The left aPHC was active in all contextual judgment task conditions. This
suggests a functional segregation, with posterior sections of the PHC supporting
visuospatial processing of scenes and anterior sections of the left PHC involved
in contextual associative processing\citep{baumann2016functional}.

%
\citep{baldassano2016two}: We propose that scene processing is fundamentally
divided into two collaborating but distinct networks
%
One is focused on the visual features of a scene image. The other is related to
contextual retrieval and navigation.
%
Under this framework, scene perception is less the function of a unified set of
distributed neural machinery and more of ``an ongoing dialogue between the
material and symbolic aspects of the past and the continuously unfolding
present'' (Baker, 2012, in The Word Hoard).

%
\citep{baldassano2016two} with respect to natural scene perception: one can
imagine at least two separable functions:
%
1) processing the specific visual features present in the current glance of a
scene,
%
2) and connecting that to the stable, high-level knowledge of where the place
exists in the world, what has happened here in the past, and what possible
actions we could take here in the future \citep{baldassano2016two}.
%
For most cognitive and physical tasks we undertake in real-world places, the
specific visual attributes we perceive are just a means to this end, of
recalling and updating information about the physical environment; ``the
essential feature of a landmark is not its design, but the place it holds in a
city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.

%
Activation maxima associated with visuospatial and mnemonic
processes were spatially segregated, providing support for the existence of
functionally distinct subregions along the PHC longitudinal axis and suggesting
that the PHC serves as a functional interface between perception and memory
systems\citep{baumann2016functional}.

Results suggests a predominantly perceptual role for the pPHC and a mnemonic
role for the anterior parahippocampal cortex (Note: the anterior parahippocampal
cortex should not be confused with the anterior portion of the parahippocampal
gyrus, which includes the perirhinal cortex; Ranganath and Ritchey,
2012.)\citep{baumann2016functional}.

We suggest that the aPHC encodes incoming information in an amodal format and
acts as an interface with other memory regions, including the hippocampal,
retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
for an review)\citep{baumann2016functional}.
